Condition-Based Maintenance for Systems based on Bayesian P-Box Component Models***

### 2016-10-06 cbm-rbd-paper.tex
RUL papers

CBM usually with directly or indirectly observable continuously measurable condition / degradation signal,
estimated time till failure (RUL) via distance of current signal level to fixed known failure threshold.
Inspection-based CBM via delay time model, modeling the time between detectable degradation and failure,
again time till failure via distance of current degradation level to fixed known failure threshold,
In both cases, maintenance decision via control limit / threshold for the signal.
%but in practice threshold often not known

@@

Furthermore, our method appropriately reflects epistemic uncertainty,
by using parametric p-boxes, an imprecise probability model, for the component models.

***epistemic vs. aleatoric uncertainty: big topic in reliability and risk

@@

@@

Example for Bayesian method in CBM with continuous monitoring: \cite{2011:elwany-et-al}
(exponential degradation model, whose parameters $\theta'$ and $\beta$ each have a prior
which is updated using the degradation signal history,
and use total expected infinite-horizon discounted cost to determine the maintenance policy)

@@

>>>>

CBM usually with directly or indirectly observable continuously measurable condition / degradation signal,
estimated time till failure (RUL) \citep{2014:rul-review, 2011:rul-review-statistical}
via distance of current signal level to fixed known failure threshold.
Inspection-based CBM via delay time model, modeling the time between detectable degradation and failure,
again time till failure via distance of current degradation level to fixed known failure threshold,
In both cases, maintenance decision via control limit / threshold for the signal, RUL not explicitely calculated.
%but in practice threshold often not known

@@

Furthermore, our method appropriately reflects epistemic uncertainty,
by using sets of conjugate priors \citep{diss} for the component models.
The resulting sets of component posteriors are equivalent to parametric p-boxes,
an imprecise probability model popular in risk and reliability engineering.

These parametric posteriors are then used to calculate the exact distribution of system RUL,
we therefore accomplish the same as \cite{2013:si-et-al} for their situation.

***figure of process: set of component priors $\to$ set of component posteriors $\to$ system RUL $\to$ $g(\tau)$ $\to$ $\tau^*$

***single $\tau^*$ vs set of $\tau^*$: decision support

***discuss \cite{2015:sankararaman}, epistemic vs. aleatoric uncertainty: big topic in reliability and risk

@@

***we go beyond what \cite{2015:sankararaman} recommends

@@

Example for Bayesian method in CBM with continuous monitoring: \cite{2011:elwany-et-al}
(exponential degradation model, whose parameters $\theta'$ and $\beta$ each have a prior
which is updated using the degradation signal history,
and use total expected infinite-horizon discounted cost to determine the maintenance policy,
RUL not explicitely calculated)

@@

\cite{2013:si-et-al} do CBM with continuous monitoring taking into account the whole degradation path history.
The authors provide exact expressions for the RUL distribution, which is updated in a Bayesian framework.
The RUL distribution is used to construct a replacement decision model using the unit cost rate
(eq. 35, citation Wang and Zhang 2005)\\
***this is most similar to what we do: exact RUL distribution $\to$ maintenance decision,
but we have component status instead of degradation signal as basis for RUL,
and we model epistemic uncertainties!\\
***check again to be sure, whot do they say about selection of prior parameters?***
